The cost of school consolidations: impacts of reduced accessibility

### 2024-04-10 paper/Manuscript.qmd
The paper still needs the appendix. I cached the code for speed.

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = '', 
  out.width = "1\\linewidth")
```

@@

>>>>

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = '', 
  out.width = "1\\linewidth")
```

@@

# Appendix

The regression model for the OTGC for schools goes here.
